Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
finished first pass at reddening discussion

Information from the spectral lines of these SSPP stars can be used, along with
 a library of synthetic stellar spectra, to predict the true optical broadband 
colors. The `true' reddening then is simply the difference in the observed
$g-r$ color and the $g-r$ color predicted from the spectral lines. This
gives us $E(B-V)$ estimates for $\sim$250,000 lines of sight, mostly at
high Galactic latitude. The calibration of two-component optical depth
to $E(B-V)$ is then performed as a linear regression of $E(B-V)_{SSPP}$ versus
$\tau_{545}$. The results of this regression are shown in Figure 
\ref{fig:calib}. Indeed there appears to be a strong linear relation
between $E(B-V)_{SSPP}$ and $\tau_{545}$ The conversion factor from 
$\tau_{545}$ to $E(B-V)$ is $\sim$2400.

>>>>

Along with a library of stellar atmosphere models, the spectral lines of these
stars can be used to predict their intrinsic optical broadband colors. The 
`true' reddening is then simply the difference in the observed $g-r$ color and
the $g-r$ color predicted from the spectral lines. Applying a 
color transformation then yields `true' $E(B-V)$ values for $\sim$250,000 lines
of sight, mostly at high Galactic latitude. The calibration of two-component 
optical depth to $E(B-V)$ is then performed as a linear regression of 
$E(B-V)_{SSPP}$ versus $\tau_{545}$. $\tau_{545}$ is considered to the 
independent variable in this regression, as we ultimately wish to predict 
$E(B-V)$ as a function of optical depth, and $\tau_{545}$ has much higher S/N 
than the SSPP $E(B-V)$ estimates.

The result of this regression is shown in Figure \ref{fig:calib}. Indeed there 
appears to be a strong linear correlation between $E(B-V)_{SSPP}$ 
and $\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
2.41$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to 
zero, $\sim$3 mmag.

Figure \ref{fig:resid} shows a two-dimensional histogram of the residuals of
the $\tau_{545}$-based $E(B-V)$ predictions relative to the corresponding
spectrum-based $E(B-V)$ predictions, as a function of SFD $E(B-V)$. Clearly 
there are some systematic trends in the residuals. Still, for 
$E(B-V)_{SFD}$$<$0.28 ($\sim$80\% of the sky), the residual median is always 
within 10 mmag of zero. Over the entire range $E(B-V)_{SFD}$$<$0.7, the 
residual median is always within 30 mmag of zero.
